### 2018-07-09 99_Documentation/11_StabFem_BasicFunctionalities.tex
birdcall data

Looking inside the file \keys{Data.ff2m}, the header (i.e.  first four lines) is as follows :
\lstinputlisting[linerange={1-5}]{../EXAMPLE_Lshape/Data.ff2m}, 
meaning that this files contains a P1 mesh-organised field called 'T'.

@@

The line 4 explains the nature of the data which is contained in the file.
There can be as many data objects as you want organised in the order of your choice. The recognized types are currently as follows :
\begin{description}
\item{ \bf P1}  for mesh-structured data stored as P1 finite-elements
\footnote{P2 data is not yet supported, the solution is to convert everything to P1 before exportation.}  
\item{\bf P1c}  for mesh-structured {\em complex} data stored as P1 finite-elements
\item{\bf real} for real scalars,
\item{\bf complex} for complex scalars,
\item{\bf real.N} for real vectors of dimension N not associated to a mesh,
\item{\bf complex.N} for complex vectors of dimension N not associated to a mesh,
\item{\bf P1s} for real data defined along a frontier of the mesh,
\item{\bf P1sc} for complex data defined along a frontier of the mesh.
\end{description}

>>>>

Looking inside the file \keys{Data.ff2m}, the header (i.e.  first four lines) is as follows :
\lstinputlisting[linerange={1-6,199}]{../EXAMPLE_Lshape/Data.ff2m}, 
meaning that this files contains a P1 mesh-organised field called 'T'.

@@

The line 4 explains the nature of the data which is contained in the file.
There can be as many data objects as you want organised in the order of your choice. The recognized types are currently as follows :
\begin{description}
\item{ \bf P1}  for mesh-structured data stored as P1 finite-elements
\footnote{P2 data is not yet supported, the solution is to convert everything to P1 before exportation.}  
\item{\bf P1c}  for mesh-structured {\em complex} data stored as P1 finite-elements
\item{\bf real} for real scalars,
\item{\bf complex} for complex scalars,
\item{\bf real.N} for real vectors of dimension N not associated to a mesh,
\item{\bf complex.N} for complex vectors of dimension N not associated to a mesh,
\item{\bf P1surf} for real data defined along a frontier of the mesh,
\item{\bf P1surfc} for complex data defined along a frontier of the mesh.
\end{description}
